Operation Manual

### 2024-10-28 docs/writing/outline.tex
Incorporating comments to outline

			\item Inconsistencies in cookie preparation, (different height, non parallel faces) (figure related) %inconsistent_cookies.jpg

@@

					\item figure

@@

						\item figure

@@

			\item 

@@

	\item opportunities for improvements

@@

		\item focus stacking
			\begin {enumerate}
			\item when a sample is microtomed, the vessels are hollow. The autofocusing algorithm can be confused from this 

@@

			\item Lenses

@@

				\item troubles with fixed aperature / non autofocusing / poorly manufactured lens
				\item lack of control to increase sharpness
				\item autofocusing with Z-axis movement is time consuming to do without image blur
				\item poor lens manufacturing can lead to drastically different quality / lighting between the edges and center of an image
				\item good lens can increase sharpness and therefore stitching accuracy and ML inference
				\item obtain similar quality between the corner and center of the image
				\item Difficulty stitching with lower detail images, can't increase digitizing speed, must downscale high resolution images 

@@

@@

@@

		\item poor lens quality seemed to be the culprit of producing visible seams when stitching with larger field of view images 

@@

	\item Software support for large files 
		\begin{enumerate}
		\item Not all software can support this, especially if the computer is RAM constrained. Ring analysis tool which uses BigTIFF, HD5, or memory maps and loads only partial portions of the full image would be useful
		\end{enumerate}
	\end{enumerate}
\item Conclusions (optional for MEE) % Usually I am anti-conclusions because you just end up repeating yourself, but I think this could work here, especially to end on a positive after the 'opportunities' section. I think you could add  the 'potential for automatic tree ring identification with iamge processing / ML ' and 'potential for vessel counts for an entire ring'  here perhaps.
	\begin{enumerate}
	\item empty
	\end{enumerate}

\end{outline}
\end{document}

>>>>

			\item Inconsistencies in cookie preparation, (different height, non parallel faces)%inconsistent_cookies.jpg
				\subitem figure for inconsistencies

@@

				\item figure for focusing 
				\item figure for sample setup ideal/realistic

@@

				\item figure for grid traverse

@@

		\item X,Y,Z imaging machine which acts as a scanner 
		\item obtains a grid of in focus images and slightly overlapping images which get stitched together to form one large mosaic 
		\item designed for other labs with minimal engineering experience or equipment to build this for themselves

@@

	\item opportunities for improvements %combine into strengths and opportunities? 

@@

		\item Software support for large files than 2.5GB >
			\item Not all software can support this, especially if the computer is RAM constrained. Ring analysis tool which uses BigTIFF, HD5, or memory maps and loads only partial portions of the full image would be useful

@@

		\item Integration with automatic tree ring identification model

@@

			\item It would be interesting to analyze the images before stitching in a different thread to potentially stitch together a binary bitmap which highlight tree rings
			\item This could potentially drop the need for a hypercomputer if inference could be made concurrently with the images being captured

@@

		\item Identifying vessel counts in each growth year 

@@

\item Conclusions (optional for MEE) % Usually I am anti-conclusions because you just end up repeating yourself, but I think this could work here, especially to end on a positive after the 'opportunities' section. I think you could add  the 'potential for automatic tree ring identification with iamge processing / ML ' and 'potential for vessel counts for an entire ring'  here perhaps.

@@

	\item empty

@@

\end{enumerate}
\end{outline}
\end{document}
